### 2021-10-29 papers/thesis/resubmitted/ch1-introduction/introduction.tex
Intro roadmap is now numbered
Added bstodo notes to indicate changes

Univariate orthogonal polynomials (hereon also referred to as OPs) have been extensively involved in the development of multiple fields of computational and applied mathematics. For example, univariate OPs have been used to derive spectral methods to numerically solve one-dimensional differential equations (see e.g. \cite{trefethen2000spectral, canuto2007spectral, gottlieb1977numerical, boyd2001chebyshev, mason2002chebyshev, shen2011spectral, olver2013fast}). While there are many famous examples of univariate OPs -- such as the Jacobi polynomials, with special cases of the Legendre polynomials and the Chebyshev polynomials but to name a few of the classical families \cite[\S18.3]{DLMF} -- the area of multivariate orthogonal polynomials has a smaller array of research.

@@

Spherical harmonics (SHs) are of course a long-established and famous group of functions defined on the surface of a sphere with certain useful properties (for example, they are orthogonal to each other on the unit sphere, have sparse recurrences, and are eigenfunctions of the spherical Laplacian) and as a result are widely used in many scientific fields for solving PDEs including computer graphics (e.g. \cite{moon2008efficient, sloan2013efficient}), astrophysics (e.g. \cite{vasil2019tensor}), quantum theory (e.g. \cite{varshalovich1988quantum}), biochemistry (e.g.\cite{parimal2014application, basko1998application}), geosciences (e.g. \cite{fletcher2017data, hollerbach2013parity}) and meteorology (e.g. \cite{evans1998spherical, rubinstein2015scalar, wedi2013fast, ecmwf2020scalability, courtier1998ecmwf, silberman1954planetary, gottlieb1977numerical}). Spectral methods on the sphere involving spherical harmonics have been used for over 60 years \cite{silberman1954planetary}. Notably, spherical harmonics are also used as basis functions for the spectral transform method that makes up part of the model in the Integrated Forecasting System (IFS), which is used by ECMWF for their forecasts \cite{wedi2013fast}.

@@

% GENERAL FRAMEWORK
The construction of the spectral methods in this thesis follow a similar pattern that is worth detailing here as a general framework.
\begin{itemize}
	\item \textit{Define the domain of interest.}

@@

		For instance, this would be useful for constructing an operator matrix that represents a variable coefficient in a Helmholtz example.
\end{itemize}

By following this framework, one will be able to write down a given PDE in spectral space (i.e. as a matrix-vector equation). The variables are given by their coefficients for their expansion in the OP basis, while the differential and other operations are given by their relevant operator matrices. The resulting system's sparsity is a result of the sparse relations of the OPs.

>>>>

\bstodoinline{Any comments in boxes like these indicate changes made.

Aside from where I have marked, I have also:

- Fixed typos pointed out and found myself

- Added commas or full stops after equations

- Changed how commas are presented in equations with \enquote{cases}

- Added round brackets to citations of equation numbers in the DLMF

- Added a dot where citing a page number (eg, p.76)

- Replaced \& with and}

Univariate orthogonal polynomials (hereon also referred to as OPs) have been extensively involved in the development of multiple fields of computational and applied mathematics. For example, univariate OPs have been used to derive spectral methods to numerically solve one-dimensional differential equations (see e.g. \cite{trefethen2000spectral, canuto2007spectral, gottlieb1977numerical, boyd2001chebyshev, mason2002chebyshev, shen2011spectral, olver2013fast}). While there are many famous examples of univariate OPs -- such as the Jacobi polynomials, with special cases of the Legendre polynomials and the Chebyshev polynomials but to name a few of the classical families \cite[\S18.3]{DLMF}\bstodo{Clarified that these families named are all Jacobi} -- the area of multivariate orthogonal polynomials has a smaller array of research.

@@

Spherical harmonics (SHs) are of course a long-established and famous group of functions defined on the surface of a sphere with certain useful properties (for example, they are orthogonal to each other on the unit sphere, have sparse recurrences, and are eigenfunctions of the spherical Laplacian \bstodo{Re-worded the properties}) and as a result are widely used in many scientific fields for solving PDEs including computer graphics (e.g. \cite{moon2008efficient, sloan2013efficient}), astrophysics (e.g. \cite{vasil2019tensor}), quantum theory (e.g. \cite{varshalovich1988quantum}), biochemistry (e.g.\cite{parimal2014application, basko1998application}), geosciences (e.g. \cite{fletcher2017data, hollerbach2013parity}) and meteorology (e.g. \cite{evans1998spherical, rubinstein2015scalar, wedi2013fast, ecmwf2020scalability, courtier1998ecmwf, silberman1954planetary, gottlieb1977numerical}). Spectral methods on the sphere involving spherical harmonics have been used for over 60 years \cite{silberman1954planetary}. Notably, spherical harmonics are also used as basis functions for the spectral transform method that makes up part of the model in the Integrated Forecasting System (IFS), which is used by ECMWF for their forecasts \cite{wedi2013fast}.

@@

% GENERAL FRAMEWORK
\bstodoinline{The following is the added "roadmap"}
The construction of the spectral methods in this thesis follow a similar pattern that is worth detailing here as a general framework.
\begin{enumerate}
	\item \textit{Define the domain of interest.}

@@

		For instance, this would be useful for constructing an operator matrix that represents a variable coefficient in a Helmholtz example.
\end{enumerate}

By following this framework, one will be able to write down a given PDE in spectral space (i.e. as a matrix-vector equation). The variables are given by their coefficients for their expansion in the OP basis, while the differential and other operations are given by their relevant operator matrices. The resulting system's sparsity is a result of the sparse relations of the OPs.
\bstodoinline{End of added roadmap}
